\chapter{Conclusion}
\markright{Conclusion}

\section{Future Work}

We plan to continue optimizing our system by incorporating future updates of
\js language, \js runtime engine and third party dependencies. The upcoming
\js standard brings a lot of promising features.  One of the new language
feature in ECMAScript 7 proposal is the native support for observing changes
to objects~\cite{jsobserveprop}. A evaluation shows that dirty checking in
AngularJS becomes 20 to 40 times faster using this
feature~\cite{angularjsspeedup}. This will greatly improve our system's
capacity to host AngularJS applications.


% improve dependency packages... 

We also plan to implement failover mechanism for   worker processes.  In
current implementation, when a worker process terminates,  the master still
dispatches requests to that worker. We need to implement a failure detection
mechanism to detect failed workers and a method to migrate the failed workers'
\appins{}s and virtual browsers to living workers.


Finally, as a PaaS platform we need a better admin interface 
to enable developers to monitor and diagnose their applications.
Currently, the admin interface only displays very basic information for deployed 
applications. We need to expose application logs 
and performance related statistics to application developers.

\section{Summary}

Maintaining the rich presentation state  of a web application server-side has
many potential benefits, ranging from simplified application development,
improved user experience, to increased security.  There is strong interest,
primarily outside of academia, in the development of platforms that simplify
cloud-based  application development.

We have prototyped and extensively tested this approach, focusing on a
scalable multiprocess version of our \cb{} platform. The key limitations we
encountered were not aspects of systems architecture or design,  but the
overhead cost of running rich frameworks, primarily in terms of CPU time.   As
these costs shift with the further refinement of these frameworks, we expect
that the use of this approach become more realistic.
