%
% PROJECT: <ETD> Electronic Thesis and Dissertation Initiative
%   TITLE: LaTeX report template for ETDs in LaTeX
%  AUTHOR: Neill Kipp, nkipp@vt.edu
%     URL: http://etd.vt.edu/latex/
% SAVE AS: etd.tex
% REVISED: September 6, 1997 [GMc 8/30/10]
% 

% Instructions: Remove the data from this document and replace it with your own,
% keeping the style and formatting information intact.  More instructions
% appear on the Web site listed above.

\documentclass[12pt]{report}

\usepackage{epsfig,endnotes}

\usepackage{color}
\usepackage{epstopdf}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{xspace}
\usepackage{booktabs}
%\usepackage{float}
\usepackage[hyphens]{url}
\usepackage{path}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{courier}
\usepackage{listings}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{multirow}


\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1in}

% Uncomment for double-spaced document.
\renewcommand{\baselinestretch}{1.5}

% \usepackage{epsf}

\begin{document}
\newcommand{\cb}{Cloud\-Browser\xspace}
\newcommand{\projectname}{Cloud\-Browser\xspace}
\newcommand{\cbtwo}{Cloud\-Browser 2.0\xspace}
\newcommand{\js}{Java\-Script\xspace}
\newcommand{\nodejs}{Node.js\xspace}
\newcommand{\appins}{App Instance\xspace}
\newcommand{\jsdom}{JSDOM\xspace}
\newcommand{\citemain}{~\cite{mcdaniel2012cloudbrowser}}
\newcommand{\etdtitle}{Rich Cloud-based Web Applications with \cbtwo}

%% A ``long'' caption.  Long captions show up in the list of
%% tables/figures with only the first argument.  Both arguments
%% show up in the actual caption.
\newcommand{\longcaption}[2]{\caption[#1]{#1 #2}}

\input{figure}

\def\code#1{\texttt{#1}}
\def\nodermi{\texttt{nodermi\xspace}}

\thispagestyle{empty}
\pagenumbering{roman}
\begin{center}

% TITLE
{\Large 
\etdtitle{}
}

\vfill

Xiaozhong Pan

\vfill

Thesis submitted to the Faculty of the \\
Virginia Polytechnic Institute and State University \\
in partial fulfillment of the requirements for the degree of

\vfill

Master of Science \\
in \\
Computer Science and Applications

\vfill

Godmar V. Back, Chair \\
Eli Tilevich\\
Ali R. Butt

\vfill

April 28, 2015 \\
Blacksburg, Virginia

\vfill

Keywords: Web, Javascript, Node.js, Distributed System
\\
Copyright 2015, Xiaozhong Pan

\end{center}

\pagebreak

\thispagestyle{empty}
\begin{center}

{\large \etdtitle{}}

\vfill

Xiaozhong Pan

\vfill

(ABSTRACT)

\vfill

\end{center}

When developing web applications using traditional methods, the developers
need to partition the application logic into a client side and server side,
then implement these two parts separately (probably in two different
programming languages) and write the communication code to synchronize
application state between the two parts. \cb is a server-centric web
framework that eliminates this need of partitioning application entirely. In
\cb, the application code is executed in server side virtual browsers
which also preserves the application's presentation state. The client web
browsers act like rendering devices, they fetch and render representation
states from the virtual browsers. The client-server communication and user
interface rendering is implemented by the framework under the hood. The
applications are developed in a way similar to regular web pages, using no
more than HTML, CSS and \js. Since the user interface state is
preserved server side, the framework also provides a continuous experience for
users who can disconnect from the application at any time and reconnect to
pick up at where they left off.

The original implementation of \cb is single-threaded  and supported
deployment on only one process. We implemented \cbtwo, a multi-process
implementation of \cb. \cbtwo can be deployed on a cluster of servers as well
as a single multi-core server. It distributes the virtual browsers to multiple
processes and  dispatches client requests to the associated virtual browsers.
\cbtwo also refines the \cb application deployment model to make the framework
a PaaS platform. The developers can develop and deploy different types of
applications and the platform will automatically make them scalable.


% To transparently partition the existing CloudBrowser infrastructure
% code across nodes, we designed and implemented an object-oriented RPC
% framework called nodermi for node.js.  Nodermi transparently creates remote
% references during remote method invocations and garbage collects remote
% references when they are not needed. To better understand the limitations of
% the system and assess the feasibility of hosting real-life applications, we
% evaluated the system's performance using different types of applications and
% JavaScript libraries. Our experiments show that CloudBrowser 2.0 scales
% linearly, it can support 2,800 concurrent clients interacting with a non-
% trivial web application using a eight core machine.

% ------------

\vfill

% GRANT INFORMATION

\pagebreak

% Dedication and Acknowledgments are both optional
% \chapter*{Dedication}
% \chapter*{Acknowledgments}
\input{acknowledgment}

\tableofcontents
\pagebreak

\listoffigures
\pagebreak

\listoftables
\pagebreak

\pagenumbering{arabic}
\pagestyle{myheadings}

\input{introduction}
\input{background}
\input{rmi}
\input{implementation}
\input{evaluation}
\input{related}
\input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\markright{Bibliography}
\bibliographystyle{plain}
\bibliography{../references,../webapps2012,../webappsadditional}
%
% Otherwise, uncomment the following:
% \chapter*{Bibliography}

% \appendix

% In LaTeX, each appendix is a "chapter"
% \chapter{Program Source}


\end{document}
